---
title: "plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Plotly of NY NOAA

```{r setup, include=FALSE}
library(tidyverse)
library(plotly)
library(readr)
library(dplyr)
```

Import data and select only 10 Weather station data from all large dataset.
```{r ,warning=FALSE}
nynoaa <- read_csv("data/nynoaadat.csv",
                   col_names = TRUE,
                   na = c("","NA")) |>
          janitor::clean_names() |>
          drop_na()

id_10 = unique(nynoaa$id)[1:10]
nynoaa$year = year(nynoaa$date)
nynoaa$month = month(nynoaa$date)

nynoaa = nynoaa|>
  filter(id==id_10) |>
  filter(year>=1981 & year <= 1990)
```

Create new year variable and month variable, and then make a bar plot about Total Precipitation (tenths of mm) in 1981 in Different Stations
```{r}
nynoaa |>
  filter(year == "1981")|>
  group_by(id)|>
  summarise(total_prcp=sum(prcp))|>
  plot_ly(
    x = ~id, y = ~total_prcp, type = "bar")|>
    layout(title = "Total Precipitation (tenths of mm) in 1981 in Different Stations")
 
```

Make a plot about Precipitation (tenths of mm) in 1990 in some special Weather station ID.  
```{r}
nynoaa |>
  filter(year == "1990")|>
  plot_ly(
    x = ~month, y = ~prcp, type = "scatter", mode = "markers",
    color = ~id,alpha = 0.5)|>
    layout(title = "Monthly Precipitation (tenths of mm) in 1990")
```

Make Boxplot for Maximum temperature from 1981 to 1990 in different stations.
```{r}
  nynoaa |> 
  plot_ly(x = ~id, y = ~tmax, color = ~id, type = "box")|>
  layout(title = "Boxplot for Maximum temperature from 1981 to 1990 in different stations")
```

